Lucy.js: Client-Side Indexes for Fast Full-Text Searching

### 2014-12-11 paper/paper.tex
Some more fixes and additions

Indexed Database (IndexedDB) is a collection of Javascript APIs and is an official W3C specification (Proposed Recommendation stage) ~\cite{w3c}. It is supported by almost every modern browser, both on desktop and mobile devices. Chrome, Firefox, Internet Explorer, Opera, and Safari are only some of the browsers that have added support for IndexedDB in their modern versions. For our implementation, we focused our testing and demos on the Chrome browser as it is currently the most widely used.
On Chrome browsers, IndexedDB interfaces with a key-value store named LevelDB built at Google in C++ and inspired by BigTable. In LevelDB, keys and values are arbitrary byte arrays and data is stored in sorted order by key. It supports batch writing, secondary indexes, \texttt{put} and \texttt{get} commands using the key, and forward and backward iteration over keys (range queries).

@@

\subsubsection{Creating a Full-Text Index}
The interface to a database is maintained through an \texttt{IDBDatabase} object.
To alter the schema of an IndexedDB database, for instance to create a new object store, the code must update the database version from its current version. This is not necessary when creating a normal secondary index on an existing object store. However, it will need to be updated when creating one of our new full-text indexes, as they are stored in IndexedDB as regular object stores. Thus the developer needs to persist locally the current version of the database and increment it before creating a new full-text index. Otherwise, the creation of a full-text index is very similar to that of a normal index. Given the \texttt{IDBObjectStore} that the index will be created on, we repurpose the existing \texttt{createIndex$\left(index\_name, key\_path\right)$} function for creating full-text indexes. We add an additional optional parameter of \texttt{type} which allows the developer to specify a type of full-text index they would like to build. The full-text index options we allow are \texttt{inverted}, \texttt{prefix}, and \texttt{suffix}. *********UPDATE If the developer does not specify a type, then a typical IndexedDB index would be created. Below is an example of JavaScript code to create an inverted index called \texttt{tweets\_text} on a field \texttt{text} in an object store of Twitter tweets.

@@

We created Lucy.js in JavaScript, as the IndexedDB API is also in JavaScript. The code consists of three main files - \texttt{lucy.js}, \texttt{invindex.js}, \texttt{trieindex.js},  and \texttt{trieindex-new.js} *********UPDATE? plus some third-party files that the user must include in their HTML file. The user should also additionally add one of the \texttt{<language>\_stopwords.js} files in order to pick a language to check stopwords on.

@@

\begin{verbatim}
for each node: 
    if node.children = 1:
        for each parent's children:
        	    if children[i] points to node:
        	    	children[i] += child.prefix;
        // number of characters to reach parent:
        child.parent++
        delete node
\end{verbatim}

@@

For the DFS case, we maintain a counter of pending paths that we pass by reference to the recursive method responsible for traversing the tree, decrement it by 1 when we reach a leaf and increment it by 1 when we encounter a subtree with more than one elements. When the counter becomes zero at a leaf, we conclude the search.

@@

We first removed unneeded information such as sentiment flags to reduce the size of the dataset, as we are only interested in textual content. We then wrote an ad-hoc Python script to select a random subset and convert it to JSON, which is what the generic IndexedDB importer we wrote expected.

After several tests with different sample sizes, we settled for about 5\% of the data (44771 tweets), since our target browser (Google Chrome) was having difficulty with larger datasets.

@@

For our 44771 tweets dataset, it took (average of 3 index creations) 3 minutes and 21 seconds to build the inverted index, 47 minutes and 24 seconds to build the prefix trie, 48 minutes and 12 seconds to build the suffix trie and 2 minutes and 53 seconds to build the hybrid prefix trie (we did not measure

@@

We tried four different queries with different result set sizes (from 25 to 2398) on index type, as well as plain sequential search, which is the only type of string search that IndexedDB offers out of the box. The results can be seen in Figure~\ref{querytimes}.

While all of our indexes have comparable performance, they outperform sequential search by several orders of magnitude. Sequential search for all four of our queries seems to be taking close to 3 seconds, whereas our index-optimized queries take only about 10-100ms.

@@

\begin{figure}[h!]
   \includegraphics[scale=.43]{trie_maxdepth_graph}
  \caption{Maximum depth vs lookup times for a prefix trie index. A depth of ``None'' indicates that there is no limit. The results for three different search terms are shown. The dataset size was roughly 2100 tweets.}
\label{comptrie}
\end{figure}

>>>>

Indexed Database (IndexedDB) is a collection of Javascript APIs for a multi-threaded, asynchronous client-side key-value store. It is an official W3C specification ~\cite{w3c}, at the Proposed Recommendation stage as of November 20th, 2014. It is supported by almost every modern browser, both on desktop and mobile devices. Chrome, Firefox, Internet Explorer, Opera, and Safari are only some of the browsers that have added support for IndexedDB in their modern versions. For our implementation, we focused our testing and demos on the Chrome browser as it is currently the most widely used.

On Chrome browsers, IndexedDB interfaces with a key-value store named LevelDB built at Google in C++ and inspired by BigTable. In LevelDB, keys and values are arbitrary byte arrays and data is stored in sorted order by key. It supports batch writing, secondary indexes, \texttt{put} and \texttt{get} commands using the key, and forward and backward iteration over keys (range queries).

@@

\subsubsection{Creating a Full-Text Index}

The interface to a database is maintained through an \texttt{IDBDatabase} object.
To alter the schema of an IndexedDB database, for instance to create a new object store, the code must update the database version from its current version. This is not necessary when creating a normal secondary index on an existing object store. However, it will need to be updated when creating one of our new full-text indexes, as they are stored in IndexedDB as regular object stores. Thus the developer needs to persist locally the current version of the database and increment it before creating a new full-text index. Otherwise, the creation of a full-text index is very similar to that of a normal index. Given the \texttt{IDBObjectStore} that the index will be created on, we repurpose the existing \texttt{createIndex$\left(index\_name, key\_path\right)$} function for creating full-text indexes. We add an additional optional parameter of \texttt{type} which allows the developer to specify a type of full-text index they would like to build. The full-text index options we allow are \texttt{inverted}, \texttt{prefix}, and \texttt{suffix}. If the developer does not specify a type, then the function call is deferred to the native IndexedDB API and a regular index would be created. Below is an example of JavaScript code to create an inverted index called \texttt{tweets\_text} on a field \texttt{text} in an object store of Twitter tweets.

@@

We created Lucy.js in JavaScript, as the IndexedDB API is also a JavaScript API. The code consists of four main files - \texttt{lucy.js}, \texttt{invindex.js}, \texttt{trieindex.js},  and \texttt{trieindex-hybrid.js} *********UPDATE? plus some third-party files that the user must include in their HTML file. The user should also additionally add one of the \texttt{<language>\_stopwords.js} files in order to pick a language to check stopwords on.

@@

\begin{verbatim}
for each node: 
   if node.children = 1:
      for each parent's children:
         if children[i] points to node:
     	    children[i] += child.prefix;
     child.parent++ (# of chars to reach parent)
     delete node
\end{verbatim}

@@

For the DFS case, we maintain a counter of pending paths that we pass by reference to the recursive method responsible for traversing the tree, decrement it by 1 when we reach a leaf and increment it by max(0, n) when we encounter a node with n+1 children. When the counter becomes zero at a leaf, we conclude the search.

@@

We first stripped off unneeded information such as sentiment flags to reduce the size of the dataset, as we are only interested in textual content. We then wrote an ad-hoc Python script to select a random subset and convert it to JSON, which is what the generic IndexedDB importer we wrote expected.

After several tests with different sample sizes, we settled for about 5\% of the original dataset (44771 tweets), as our target browser (Google Chrome) was having difficulty with larger datasets.

@@

For our 44771 tweets dataset, it took (average of 3 index creations) 3 minutes and 21 seconds to build the inverted index, 47 minutes and 24 seconds to build the prefix trie, 48 minutes 12 seconds to build the suffix trie, 2 minutes 53 seconds to build a hybrid prefix trie and 3 minutes 2 seconds to build a hybrid suffix tree.

@@

We tried four different queries with different result set sizes (from 25 to 2398) on index type, as well as plain sequential search, which is the only type of string search that IndexedDB provides out of the box. The results can be seen in Figure~\ref{querytimes}.

While all of our indexes have comparable performance, they outperform sequential search by orders of magnitude. Sequential search for all four of our queries seems to be taking close to 3 seconds, whereas our index-optimized queries take only about 10-100ms.

@@

\begin{figure}[h!]
   \includegraphics[scale=.38]{trie_maxdepth_graph}
  \caption{Maximum depth vs lookup times for a prefix trie index. A depth of ``None'' indicates that there is no limit. The results for three different search terms are shown. The dataset size was roughly 2100 tweets.}
\label{comptrie}
\end{figure}
